% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Pei-ZENG-CV-2016-06
%% <https://github.com/qubiter/pei-cv>
%% This is Pei Zeng's CV (long version).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Adopted the SIMPLE-RESUME-CV template
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,MMMyyyy,nonstop]{simpleresumecv}
% Class options:
% a4paper, letterpaper, draft, nonstop
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy
\usepackage{amsmath}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Pei Zeng}
\newcommand{\CVTitle}{Pei Zeng's Resume}
\newcommand{\CVNote}{CV compiled on {\today} in English.(long version)}
\newcommand{\CVWebpage}{http://www.github.com/qubiter/pei-cv}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
%\href{https://www.google.com/maps/place/17+Prime+Avenue,+Springfield,+Pennsylvania+10111,+USA}
%{School of Physics, Nanjing University Gulou Campus, Jiangsu Province, China}
School of Physics, Nanjing University Gulou Campus, Jiangsu Province, China, 210093
\par
\href{peizeng@live.com}
{peizeng@live.com}
%\,\SubBulletSymbol\,
%+(86)\,158\,5181\,7007
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\CVWebpage}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.nju.edu.cn}
{\textbf{Nanjing University}},
Nanjing, Jiangsu, China

\GapNoBreak
\BulletItem
Bachelor of Science (B.S.) in
\href{http://physics.nju.edu.cn/}
{Physics} (minor in Acoustics)
\hfill
\DatestampYMD{2012}{09}{01} --
\DatestampYMD{2016}{06}{20}
\begin{detail}
\SubBulletItem
Cumulative GPA: 4.536 / 5.0 (Ranking: 8/182)
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}


\textbf{Physics Experiment Teaching Center},
Nanjing University

\GapNoBreak
\BulletItem
Undergraduate Research Student, Physics Department
\hfill
\DatestampYMD{2012}{12}{01} --
\DatestampYMD{2014}{05}{01}
\begin{detail}
\SubBulletItem
Project 1: Work on the 2013 IYPT problems
\SubBulletItem
Supervisor: 
Prof. Sihui Wang
\SubBulletItem
IYPT problems concerns some daily physical phenomenon. I’ve accomplished some works on ‘Jet and Film’, ‘Carbon Microphone’ and ‘Levitation’, some of which are published in the ‘Collection of works for IYPT problems(25th-26th)’ by World Scientific Press.
\end{detail}

\GapNoBreak
\begin{detail}
\SubBulletItem
Project 2: Improvement in Measuring Tiny Displacement with Double Gratings
\SubBulletItem
Supervisor: 
Prof. Huijun Zhou
\SubBulletItem
A new method to reconstruct the motion process of grating based on anti-solving the ‘cos’ equation. The work was published in Chinese magazine ‘College Physics’ in 2016.
\end{detail}

\Gap

\href{http://slab.nju.edu.cn/}
{\textbf{Dieletric Superlattice Laboratory}},
Nanjing University

\GapNoBreak
\BulletItem
Undergraduate Research Student, Physics Department
\hfill
\DatestampYMD{2014}{05}{15} --
\DatestampYMD{2016}{02}{01}
\begin{detail}
\SubBulletItem
Project: A Feasible Design of Decimeter-size Sub-wavelength Metalens
\SubBulletItem
Supervisor: 
Dr. Shuming Wang, Associate Researcher
\SubBulletItem
Partly supported by National Training Programs of Innovation for Undergraduates.
\SubBulletItem
Realizing far-field sub-wavelength imaging in mid-infrared band. Using silver microstructure for phase compensation; hyperbolic material for sub-wavelength propagation.
\SubBulletItem
Received Certification from National Training Programs of Innovation for Undergraduates with rating ``Excellent''. Reveived A patent for the Metalens design.
\SubBulletItem
Also took part in some other related works in the lab, including the design of wheeler delayed-choice experiment in SPP system; the simulation of nonlinear effect using COMSOL, etc.
\end{detail}

\Gap

\href{https://groups.oist.jp/light}
{\textbf{Light-Matter Interaction Unit}},
Okinawa Institute of Science and Technology

\GapNoBreak
\BulletItem
Research Intern
\hfill
\DatestampYMD{2015}{10}{17} --
\DatestampYMD{2016}{12}{28}
\begin{detail}
\SubBulletItem
Project: Optomechanical Effect Detection in Slotted Tapered Fiber
\SubBulletItem
Supervisors:
Prof. Sile Nic Chormaic, Dr. Yong Yang
\SubBulletItem
Observe Optomechanical effect in Slotted Tapered Optical Nanofiber using the Mach-Zender Interferometer. Try to couple the optical mode and mechanical mode using the modulated 1550nm laser amplified by EDFA.
\SubBulletItem
Completed the constrction of MZI both in free space and with in-fibre design. Made the in-fibre MZI sensitive enough for acoustic phonon detection in the fibre. (Homodyne Detection, PZ control)
\SubBulletItem
Also learned how to make silicon and $As_2S_3$ nanosphere using $CO_2$ laser(10.6um) and how to test the Whisper Gallery Mode in it.
\end{detail}

\Gap

\href{http://ese.nju.edu.cn/ICAIS/}
{\textbf{Integrated Circuit and Intelligent System Lab}},
School of Electronic Science and Engineering, Nanjing University

\GapNoBreak
\BulletItem
Undergraduate Research Student, Physics Department.
\hfill
\DatestampYMD{2016}{02}{15} --
\DatestampYMD{2016}{05}{20}
\begin{detail}
\SubBulletItem
Project: Algorithm Test and A Digital Circuit Design of The DeSTIN Deep Learning Frame
\SubBulletItem
Supervisors:
Prof. Zhongfeng Wang, Dr. Jun Lin
\SubBulletItem
Worked as my bachelor thesis project. More info on \href{https://github.com/qubiter/Bachelor-Thesis-Chinese}{\underline{Bachelor Thesis on Github(Chinese)}}.
\SubBulletItem
Tested a new deep learning frame: Deep SpatioTemporal Inference Network(DeSTIN) using MATLAB and Python;
\SubBulletItem
Exerted the EDA tool to design a Digital Circuit for the core algorithm in DeSTIN, programmed in Verilog HDL.
\end{detail}


%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section
{Publications}
{Publications}
{PDF:Publications}

\subsection
{Journals}
{Journals}
{PDF:Journals}

\GapNoBreak
\NumberedItem{[1]}
\href{http://www.cnki.net/kcms/detail/detail.aspx?DbCode=CJFQ&dbname=CJFDLAST2016&filename=DXWL201601016&uid=WEEvREcwSlJHSldSdnQ0SWZ2dGI4SEhQemFnWXVOK0VMNTJLSjdyRGFmeEZzNmhzZnp6MFpJRzFnSUJpeVVTaklBPT0=$9A4hF_YAuvQ5obgVAqNKPCYcEjKensW4IQMovwHtwkF4VYPoHbKxJw!!}
{CHEN Si, \underline{ZENG Pei}, ZHOU Hui-jun, and WANG si-hui,
``Improvement and application on method of measuring
the tiny displacement with double grating''
\textit{College Physics},
vol.~35,
no.~1,
pp.~53--56,
\DatestampYM{2016}{01}.}

% Note the use of {\CharSpace} for aligning shorter numbers.
\Gap
\NumberedItem{[2]}
\href{http://www.worldscientific.com/worldscibooks/10.1142/9355}
{Sihui Wang and Wenli Gao,
``International Young Physicists\' Tournament, Problems and Solutions 2012–2013''
\textit{World Scientific Press},
chapter.~10,~12,
\DatestampYM{2014}{12}.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
\textbf{Silver Medal} of \href{http://www.uphysicsc.com/2013contest.html}{4th University Physics Competition}
(hosted by America Physics Society and American Astronomical Society)
\hfill
\DatestampYMD{2013}{12}{13}
\begin{detail}
\SubItem
For works on the Problem B. Extraterrestrial Life.
\end{detail}

\Gap
\BulletItem
\textbf{Second Prize} 
of 4th China Undergraduate Physics Tournament
\hfill
\DatestampYMD{2013}{08}{13}

\Gap
\BulletItem
\textbf{Second Prize}
of China Undergraduate Mathematical Contest in Modeling
\hfill
\DatestampYMD{2014}{12}{15}

\Gap
\BulletItem
\textbf{Industrial Responsibility Scholarship}(RMB5000)(for top $5\%$),
\hfill
\DatestampYMD{2013}{10}{15}

\Gap
\BulletItem
\textbf{People's Scholarship}(RMB2000)(for top $10\%$),
\hfill
\DatestampYMD{2014}{10}{15}

\Gap
\BulletItem
\textbf{National Schoarship}(RMB8000)(for top $1\%$),
\hfill
\DatestampYMD{2015}{10}{15}


%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\textbf{Focus Society},
Nanjing University

\GapNoBreak
\begin{detail}
\BulletItem
The society mainly focus on life topic and literature, making newspaper 2~3 times every semester from the discussion of society members and other interested students who take part in.
\end{detail}
\BulletItem
Member in Editoring Minister
\hfill
\DatestampYMD{2012}{10}{08} --
\DatestampYMD{2013}{06}{20}
\BulletItem
Chief Editor
\hfill
\DatestampYMD{2013}{06}{20} --
\DatestampYMD{2014}{06}{20}
\begin{detail}
\SubBulletItem
Organized the content planning and type setting, and completed the final modification of 5 Focus newspapers as the chief editor, which received good rating in my department.
\SubBulletItem
Arranged 2~3 times of `type setting with CorelDraw and Photoshop' workshop inside the Focus society.
\SubBulletItem
Arranged a Society travel to Soochow City; Participated in 2~3 travel activities (Xitang City in Zhejiang Province; Mount Qixia in Nanjing, etc.).
\end{detail}

\textbf{Young Volunteers' Association},
Physics Department
\BulletItem
Member
\hfill
\DatestampYMD{2012}{10}{01} --
\DatestampYMD{2013}{06}{20}
\begin{detail}
\SubBulletItem
Organized/ Joined in 3 times of `Enlight Science among Pupils' activities, which mainly aim to popularize science knowledge and inspire the interest in Science among pupils.
\end{detail}

\textbf{Student Research Training Program's Society},
Nanjing University
\BulletItem
Member
\hfill
\DatestampYMD{2013}{10}{20} --
\DatestampYMD{2014}{06}{20}
\begin{detail}
\SubBulletItem
Organized the `XiaoXiongLunDao' activities once, acting as a small platform for communication among students and professors who work in the same academic topics. The `XiaoXiongLunDao' I arranged mainly focus on `Architecture and Space Design'.
\end{detail}


%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Chinese: Native language.

\GapNoBreak
\BulletItem
English: Fluent (speaking, reading, writing, listening).

\GapNoBreak
\BulletItem
Japanese: Basic (listening, reading, speaking).

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

\BulletItem Software and Coding:
\SubBulletItem Intermediate Proficiency: MATLAB, {\TeX}, COMSOL Multiphysics.
\SubBulletItem Basic Proficiency: Python, C, Mathematica, Verilog HDL,  Adobe Photoshop.


%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Acoustic Guitar,
Singing(karaoke),
Jogging,
Anime,
Ballroom Dancing(Modern).

%%%%%%%%%%%%%%%%%%%%%%%%
%% STANDARDIZED TESTS %%
%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Standardized Tests}
{Standardized Tests}
{PDF:Standardized Tests}

\BulletItem
TOEFL(iBT): 94(Reading 25, Listening 25, Speaking 19, Writing 25)
\hfill
\DatestampYMD{2014}{03}{22}

\BulletItem
GRE(General): Verbal 147, Quantitative 170, Analytical Writing 3.5
\hfill
\DatestampYMD{2015}{04}{18}

\BulletItem
CET-4: 581
\hfill
\DatestampYMD{2013}{06}{20}

\BulletItem
CET-6: 520
\hfill
\DatestampYMD{2013}{12}{20}

\BulletItem
Computer Level Test(level 2, C-language): Fine
\hfill
\DatestampYMD{2013}{12}{20}


%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Dr. Shuming Wang}
\newline
Assosiate Researcher in Dieletric Superlattice Laboratory,
\newline
Quantum Plasmonics and Metamaterials,
\newline
Nanjing University, National Laboratory of Solid State Microstructure
\newline
No.15 Jinyinjie, Nanjing City, Jiangsu, China 210008
\newline
\href{wangshuming@nju.edu.cn}
{wangshuming@nju.edu.cn}

\BigGap
\BulletItem
\textbf{Prof. Sile Nic Chormaic}
\newline
Principle Investigator in Light-Matter Interaction Unit
\newline
Okinawa Institute of Science and Technology
\newline
1919-1 Tancha, Onna-son, Kunigami-gun, Okinawa, Japan 904-0495
\newline
\href{sile.nicchormaic@oist.jp}
{sile.nicchormaic@oist.jp}

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]%
\hspace{2.0mm}\null

\end{document}
